Seldin Report: Ssec Scores

### 2022-07-17 SeldinReport_fix.Rmd
getting there

write.csv(ts_Ssec_brain, "Target_TESec_Ssec_brain.csv")
write.csv(ts_Ssec_liver, "Target_TESec_Ssec_liver.csv")
write.csv(tsns_Ssec_brain, "Target_TENSec_Ssec_brain.csv")
write.csv(tsns_Ssec_liver, "Target_TENSec_Ssec_liver.csv")

@@

@@

@@

numtarget_brain = c(s.brain_1top, s.brain_2top, s.brain_3top, s.brain_4top, s.brain_5top, s.brain_6top)

@@

fin_brain = data.frame(names_brain, selected_brain[,2], numtarget_brain)

fin_liver = data.frame(names_liver, selected_liver[,2], s.liver_1top)

@@

>>>>

#setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
#setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")

#write.csv(ts_Ssec_brain, "Target_TESec_Ssec_brain.csv")
#write.csv(ts_Ssec_liver, "Target_TESec_Ssec_liver.csv")
#write.csv(tsns_Ssec_brain, "Target_TENSec_Ssec_brain.csv")
#write.csv(tsns_Ssec_liver, "Target_TENSec_Ssec_liver.csv")

@@

#setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")
te.sec.b_table = read.csv("eQTL_BrainTESec_added_table.csv")
te.sec.l_table = read.csv("eQTL_LiverTESec_added_table.csv")
te.sec.b_table = fix.read.csv(te.sec.b_table)
te.sec.l_table = fix.read.csv(te.sec.l_table)

@@

eqtl.brain = te.sec.b_table[te.sec.b_table$RNAseq.Gene.Name %in% names_brain,]
eqtl.brain = eqtl.brain[selected_brain$Gene_symbol,]

eqtl.liver = te.sec.l_table[te.sec.l_table$RNAseq.Gene.Name %in% names_liver,]

@@

numtarget_brain = c(length(s.brain_1top), length(s.brain_2top), length(s.brain_3top), length(s.brain_4top), length(s.brain_5top), length(s.brain_6top))

@@

fin_brain = data.frame(Gene = selected_brain$Gene_symbol, Gene_Symbol = names_brain, Ssec_Score = selected_brain[,2], Number_Target_Genes = numtarget_brain, eQTL_FDR = eqtl.brain$fdr, eQTL_pval = eqtl.brain$pval)

fin_liver = data.frame(Gene = selected_liver$Gene_symbol, Gene_Symbol = names_liver, Ssec_score = selected_liver[,2], Number_Target_Genes = length(s.liver_1top), eQTL_FDR = eqtl.liver$fdr, eQTL_pval = eqtl.liver$pval)

@@

write.csv(fin_brain, "Summary_Table_topSsec_brain.csv")
write.csv(fin_liver, "Summary_Table_topSsec_liver.csv")
